---
title: "Alexithymia and Music perception GLMM: Cognition and Emotion Revise and Resubmit"
output:
  html_notebook: default
  pdf_document: default
---
#Revise and Resubmit Analysis 

Additional Analyses as requested 

Note: Data was collected as part of a larger project which contained depression scores, these have been included upon reviewer comments highlighting need to control for mood. 

```{r import and clean}
xfun::pkg_attach2("tidyverse")
setwd("/Users/joellarwood/Desktop/git/Negative Valence Specific Deficit in Music Affect Perception in Alexithymia")
raw <- read_csv("data/Alexithymia Music Perception and LIWC.csv")

names(raw)

reduced <- raw %>% select(contains("ID"),
                          contains("Finished"),
                          contains("MUAR"),
                          contains("MUVA"),
                          contains("TAS"),
                          contains("DASS"),
                          contains("age"),
                          contains("gender"),
                          contains("Exp"),
                          contains("play"),
                          contains("Hours"),
                          contains("Genre"),
                          contains("WC"),
                          contains("emo"),
                          -contains("Page")) %>% drop_na("ProlificID") %>% filter(Finished == 1)

names(reduced)
#check na removed in prolific id

sum(is.na(reduced$ProlificID))

#ensure only complete data is present 

table(reduced$Finished)

#count p's
nrow(reduced)

#visualise missing data 
xfun::pkg_attach2("naniar")

reduced %>% select(contains("MUVA"),
                   contains("MUAR"),
                   contains("TAS"),
                   contains("DASS")) %>% vis_miss()

#no missing data 
```
create woring data frame 'cleanrr' for analysis 
```{r}
cleanrr <- reduced
```

#make lexicon counts 

```{r lexicon}
cleanrr$pos.lex.count <- ((cleanrr$posemo*cleanrr$WC)/100)
#round 
cleanrr$pos.lex.count <- round(cleanrr$pos.lex.count, digits = 0)

cleanrr$neg.lex.count <- ((cleanrr$negemo*cleanrr$WC)/100)
cleanrr$neg.lex.count <- round(cleanrr$neg.lex.count, digits = 0)

cleanrr$emo.lex.count <- cleanrr$neg.lex.count + cleanrr$pos.lex.count

xfun::pkg_attach2("psych")

psych::describe(select(cleanrr, contains("count")))

```

#Get music scores 
```{r music score creation}
##--------Music Ratings
#Sad Music 
#Valence
cleanrr$sad.valence <- (cleanrr$MUVA31_1 + cleanrr$MUVA109_1) / 2

#AROUSAL 
cleanrr$sad.arousal <- (cleanrr$MUAR31_1 + cleanrr$MUAR109_1) / 2

#Angry music 
#Valence 
cleanrr$angry.valence <- (cleanrr$MUVA1_1 + cleanrr$MUVA69_1) / 2
#AROUSAL
cleanrr$angry.arousal <- (cleanrr$MUAR1_1 + cleanrr$MUAR69_1) / 2

#Fear Music
#VALENCE
cleanrr$fear.valence <- (cleanrr$MUVA11_1 + cleanrr$MUVA14_1) / 2
#AROUSAL
cleanrr$fear.arousal <- (cleanrr$MUAR11_1 + cleanrr$MUAR14_1) / 2

#Happy Music 
#VALENCE
cleanrr$happy.valence <- (cleanrr$MUVA23_1 + cleanrr$MUVA105_1) / 2 
#AROUSAL
cleanrr$happy.arousal = (cleanrr$MUAR23_1 + cleanrr$MUAR105_1) / 2


#Tender music 
#VALENCE
cleanrr$tender.valence <- (cleanrr$MUVA41_1 + cleanrr$MUVA42_1) / 2 
#AROUSAL
cleanrr$tender.arousal <- (cleanrr$MUAR41_1 + cleanrr$MUAR42_1) / 2 
```

#describe songs
```{r}
cleanrr %>% select(contains("valence"),
                   contains("arousal")) %>% psych::describe()
```
#Create scores 
## Alexithymia and subscales 
```{r alexithymia}
##-------create alexithymia

#Reverse scoring 
cleanrr$TAS4_1r <- 6 - cleanrr$TAS4_1
cleanrr$TAS5_1r <- 6 - cleanrr$TAS5_1
cleanrr$TAS10_1r <- 6 - cleanrr$TAS10_1
cleanrr$TAS18_1r <- 6 - cleanrr$TAS18_1
cleanrr$TAS19_1r <- 6 - cleanrr$TAS19_1

#psych::describe(clean$alexithymia)
#Difficulty identifying feelings
DIF <- c("TAS1_1", "TAS3_1", "TAS6_1", "TAS7_1", "TAS9_1", "TAS13_1", "TAS14_1")
cleanrr %>% select(DIF) %>% alpha()
cleanrr$DIF <- cleanrr %>%  select(DIF) %>% rowSums() 

#Difficulty describing feelibgs 
DDF <- c("TAS2_1", "TAS4_1r", "TAS11_1", "TAS12_1", "TAS17_1")
cleanrr %>% select(DDF) %>% alpha()
cleanrr$DDF <- cleanrr %>% select(DDF) %>% rowSums()

#Externally oriented thinking
EOT <- c("TAS5_1r", "TAS8_1", "TAS10_1r", "TAS15_1", "TAS16_1", "TAS18_1r", "TAS19_1r", "TAS20_1")
cleanrr %>% select (EOT) %>% alpha()
cleanrr$EOT <- cleanrr %>% select(EOT) %>% rowSums()

#TAS total 
cleanrr %>% select(DIF, DDF, EOT) %>% alpha()
cleanrr$alexithymia <- cleanrr %>% select(DIF, DDF, EOT) %>% rowSums()

#dichotomoize at 51 (> 51 is nonclinical) 
xfun::pkg_attach2("sjmisc")
cleanrr$clinicalalex <- dicho(cleanrr$alexithymia, dich.by = 50)
cleanrr$clinicalalex<- factor(cleanrr$clinicalalex,
                                 levels = c(0,1),
                                 labels = c("below 51", "above 51"))
#get descriptives

cleanrr %>% select(alexithymia, DIF, DDF, EOT) %>% describe()
table(cleanrr$clinicalalex)
```

#create DASS - depression subscale 
```{r}
D <- c("DASS3_1", "DASS10_1", "DASS13_1", "DASS16_1", "DASS17_1", "DASS21_1")
cleanrr %>% select(D) %>% alpha()
cleanrr$depression <- cleanrr %>% select(D) %>% rowSums()
describe(cleanrr$depression)
```
#TOSTER analysis 
```{r TOST}
TOSTER::powerTOSTr(alpha = .05, statistical_power = .8, N = 162) #bounds = +/- .228
```
## All words
```{r total tost}
#total emotions
TOSTER::TOSTr(n = 162, r = -.05, low_eqbound_r = -.228, high_eqbound_r = .228) 
```
## Positive words
```{r positive tost}
#positive emotions  
TOSTER::TOSTr(n = 162, r = -.13, low_eqbound_r = -.228, high_eqbound_r = .228) 
```
## Negative words
```{r negative tost}
#negative emotions
TOSTER::TOSTr(n = 162, r = .02, low_eqbound_r = -.228, high_eqbound_r = .228)  

```

#Reshape data to long
```{r}
#give easy ID 

cleanrr$id <- (seq.int(nrow(cleanrr)))

#arousal data
rr.long.arousal <-  gather(data = cleanrr, key = condition, value = arousal, sad.arousal, happy.arousal, fear.arousal, tender.arousal, angry.arousal, factor_key=TRUE)
rr.long.arousal <- rr.long.arousal %>% select(contains("ID"),
                                        contains("alexithymia"),
                                        contains("condition"),
                                        contains("arousal"),
                                        contains("depression"))
xfun::pkg_attach2("plyr")

rr.long.arousal$condition <- mapvalues (rr.long.arousal$condition, from = c ("sad.arousal", "happy.arousal", "fear.arousal", "tender.arousal", "angry.arousal"), to = c("Sad", "Happy", "Fearful", "Tender", "Angry"))

#valence data
rr.long.valence <- gather(data = cleanrr, key = condition, value = valence, sad.valence, happy.valence, fear.valence, tender.valence, angry.valence, factor_key=TRUE)
rr.long.valence <- rr.long.valence %>% select(contains("ID"),
                                        contains("alexithymia"),
                                        contains("condition"),
                                        contains("depression"),
                                        contains("valence"))

rr.long.valence$condition <- mapvalues (rr.long.valence$condition, from = c ("sad.valence", "happy.valence", "fear.valence", "tender.valence", "angry.valence"), to = c("Sad", "Happy", "Fearful", "Tender", "Angry"))
```

#GLMM 
Build up from nothing 
## Arousal data
```{r arousal data}
xfun::pkg_attach2("lme4")

arousalnull <- glmer(arousal ~ 1 + (1|id), data = rr.long.arousal)
arousaldep <- glmer(arousal ~ 1 + depression + (1|id), data = rr.long.arousal)
arousaldepalex <- glmer(arousal ~ 1 + depression + alexithymia + (1|id), data = rr.long.arousal)
arousaldepalexcond <- glmer(arousal ~ 1 + depression + alexithymia + condition + (1|id), data = rr.long.arousal)
arousalinteract <- glmer(arousal ~ 1 + depression + alexithymia + condition + alexithymia*condition + (1|id), data = rr.long.arousal)
arousal3interact <- glmer(arousal ~ 1 + depression + alexithymia + condition + alexithymia*condition + alexithymia*condition*depression + (1|id), data = rr.long.arousal)

anova(arousalnull, arousaldep, arousaldepalex, arousaldepalexcond, arousalinteract, arousal3interact) 

#interaction model is best fit 

xfun::pkg_attach2("sjPlot")

sjPlot::tab_model(arousalinteract)

xfun::pkg_attach2("interactions")

interactions::sim_slopes(model = arousalinteract, pred = alexithymia , modx = condition, confint = TRUE)

xfun::pkg_attach2("jtools")

interactions::interact_plot(model = arousalinteract, pred = alexithymia, modx = condition, interval = TRUE) + 
  theme_apa() + 
  geom_hline(yintercept = 0, linetype = "dotted") + labs (x = "Alexithymia", y = "Rated Arousal") 
```

## Valence data 
```{r valence glmm}
valencenull <- glmer(valence ~ 1 + (1|id), data = rr.long.valence)
valencedep <- glmer(valence ~ 1 + depression + (1|id), data = rr.long.valence)
valencedepalex <- glmer(valence ~ 1 + depression + alexithymia + (1|id), data = rr.long.valence)
valencedepalexcond <- glmer(valence ~ 1 + depression + alexithymia + condition + (1|id), data = rr.long.valence)
valenceinteract <- glmer(valence ~ 1 + depression + alexithymia + condition + alexithymia*condition + (1|id), data = rr.long.valence)
valence3interact <- glmer(valence ~ 1 + depression + alexithymia + condition + alexithymia*condition + alexithymia*condition*depression + (1|id), data = rr.long.valence)

anova(valencenull, valencedep, valencedepalex, valencedepalexcond, valenceinteract, valence3interact) 

#interaction model is best fit 

xfun::pkg_attach2("sjPlot")

sjPlot::tab_model(valenceinteract)

xfun::pkg_attach2("interactions")

interactions::sim_slopes(model = valenceinteract, pred = alexithymia , modx = condition, confint = TRUE)

xfun::pkg_attach2("jtools")

interactions::interact_plot(model = valenceinteract, pred = alexithymia, modx = condition, interval = TRUE) + 
  theme_apa() + 
  geom_hline(yintercept = 0, linetype = "dotted") + labs (x = "Alexithymia", y = "Rated valence") 
```
